---
title: "p8105_hw5_niz2000"
author: "Nora Zakaria"
date: "11/11/2019"
output: github_document
---

# Problem 1

## Load Tidyverse and the Iris Data
```{r Load Iris Data}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
iris_with_missing
```


## Function to Replace Missing Values
```{r Function to Replace Missing Values}
replace_missing = function(x) {
  if (is.numeric(x)) {
    ifelse(is.na(x), mean(x, na.rm = TRUE), x)
  } else if (is.character(x)) {
    ifelse(is.na(x), "virginica", x)
  }
}
iris_complete = map_df(iris_with_missing, replace_missing)
iris_complete
```


# Problem 2

## Load in the HW 5 Zipfile Data
```{r Load Zipfile Data}
data_df = tibble(
  participant = list.files(path = "./data")
)
data_df
```


## Iterate over Files Names
```{r Iterate Over File Names} 
data_df = function(path){
  case_control_df = read_csv(path)
  case_control_df 
}
directory = "./data"
study_df = tibble(
  observation = list.files(path = "./data"),
    files = str_c(directory, "/",observation)) %>%
  mutate(
    weekly_data = map(files, read_csv),
    observation = str_replace(observation, ".csv","")) %>%
  unnest() %>%
  rename(participant_id = observation) %>%
  mutate(
    study_arm = if_else(participant_id %in% c("con_01", "con_02", "con_03", "con_04", "con_05",
        "con_06", "con_07", "con_08", "con_09", "con_10"), "control", participant_id),
    study_arm = if_else(study_arm %in% c("exp_01", "exp_02", "exp_03", "exp_04", "exp_05",
        "exp_06", "exp_07", "exp_08", "exp_09", "exp_10"), "experimental", study_arm)) %>%
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "weekly_data") %>%
  mutate(week = str_replace(week, "week_", "")) %>%
  select(-files)
study_df
```
 
 subject_id = str_replace(subject_id, ".csv" , ""),
 week = str_replace(week, "week_", ""),
 study_arm = str_replace(study_arm, "con","control"),
 study_arm = str_replace(study_arm, "exp","experimental"),
    
## Spaghetti Plot of Observations for Each Subject Over Time
```{r Spaghetti Plot}
study_df %>% 
  group_by(participant_id, week) %>% 
  ggplot(aes(x = week, y = weekly_data, group = participant_id, color = study_arm)) +
  geom_line() +
  labs(caption = "Observations for Each Subject Over Time") + 
  viridis::scale_color_viridis(
    discrete = TRUE)
```


# Problem 3

## Set the Regression Design Elements
```{r Regression}
linear_regression= function(n = 30, beta0 = 2, beta1 = 0) {
  regression_data = tibble(
    x = rnorm(n, mean = 0, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 50^0.5)
  )
  ls_fit = lm(y ~ x, data = regression_data) 
  broom::tidy(ls_fit) %>%
    filter(term == "x")
}

#Function for Beta 1 = 0
  regression_results = rerun(100, linear_regression()) %>%
    bind_rows()
  
#Function for Beta 1 = 0 - 6
  results = tibble(
    beta1 = c(0, 1, 2, 3, 4, 5, 6)) %>%
    mutate(
      output_list = map(.x = beta1, ~rerun(100, linear_regression(beta1 = .x))),
      estimate_dfs = map(output_list, bind_rows)) %>%
    select(-output_list) %>%
    unnest(estimate_dfs)
results
```


## Plot Showing the Proportion of Times the Null was Rejected

```{r Effect Size and Power}
results %>%
  mutate(rejection = cut(p.value, breaks=c(0, 0.05, Inf), 
    labels=c("Rejected", "Not_Rejected"))) %>%
  group_by(beta1, rejection) %>%
  summarise(count = n()) %>%
  mutate(
    proportion = count / sum(count),
    as.character(beta1)) %>%
  filter(rejection == "Rejected") %>%
  #distinct(.keep_all = TRUE) %>%
  ggplot(aes(x = beta1, y = proportion)) + 
    geom_point(aes(color = "viridis"), show.legend = FALSE) + 
    geom_line(aes(color = "viridis"), show.legend = FALSE) +
    labs(
      title = "Association Between Effect Size and Power",
      x = "Beta1 True Value",
      y = "Proportion of Null Rejection")  +
    viridis::scale_color_viridis(discrete = TRUE) 
results
```
 

## Plot Showing the Average Estimate and True Value of Beta 1





